\begin{rSection}{Publications}


% \begin{pubSubsection}{Submitted / In Preparation}
% \end{pubSubsection}

\begin{pubSubsection}{International Journal}

  \item \underline{\textbf{Myung-Hwan Jeon}}, Jeongyun Kim, Sangwoo Jung, Wooseong Yang, Minwoo Jung, Jaeho Shin, and Ayoung Kim, “TRansPose: Large-Scale Multispectral Dataset for Transparent Object”, in International Journal of Robotics Research (IJRR), Accepted.

  \item Sangwoo Jung, Hyesu Jang, Minwoo Jung, Ayoung Kim, and \underline{\textbf{Myung-Hwan Jeon}}, “Imaging radar and LiDAR Image Translation for 3-DOF Extrinsic Calibration”, in Intelligent Service Robotics (ISR), Under review. \underline{\textbf{$\ast$Corresponding Author}}.

  \item \underline{\textbf{Myung-Hwan Jeon}}, Jeongyun Kim, Jee-Hwan Ryu, and Ayoung Kim, “Ambiguity-Aware Multi-Object Pose Optimization for Visually-Assisted Robot Manipulation”, in IEEE Robotics and Automation Letters (RA-L), 2022.
  
  \item Eon-ho Lee, Byungjae Park, \underline{\textbf{Myung-Hwan Jeon}}, Hyesu Jang, Ayoung Kim and Sejin Lee, “Data augmentation using image translation for underwater sonar image segmentation”, in PLoS ONE 17(8), 2022.
  
  \item Joowan Kim, \underline{\textbf{Myung-Hwan Jeon}}, Younggun Cho, Ayoung Kim, “Dark Synthetic Vision: Lightweight Active Vision to Navigate in the Dark”, in IEEE Robotics and Automation Letters (RA-L), 2021.
  
  \item \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “PrimA6D: Rotational Primitive Reconstruction for Enhanced and Robust 6D Pose Estimation”, in IEEE Robotics and Automation Letters (RA-L), 2020.  

\end{pubSubsection}

\begin{pubSubsection}{International Conference}


  \item Dong-Guw Lee, \underline{\textbf{Myung-Hwan Jeon}}, Younggun Cho, and Ayoung Kim, “Edge-guided Multi-domain RGB-to-TIR image Translation for Training Vision Tasks with Challenging Labels ”, in IEEE International Conference on Robotics and Automation (ICRA), 2023.

  \item Seungsang Yun, Minwoo Jung, Jeongyun Kim, Sangwoo Jung, Younghun Cho, \underline{\textbf{Myung-Hwan Jeon}}, Giseop Kim, and Ayoung Kim, “STheReO: Stereo Thermal Dataset for Research in Odometry and Mapping”, in IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2022
  
  \item Eon-Ho Lee, \underline{\textbf{Myung-Hwan Jeon}}, Hyesu Jang, Byungjae Park, Ayoung Kim, and Sejin Lee, “Study on the Training Effectiveness of Deep Learning with Synthesized Underwater Sonar Image Using Pix2Pix and FCN”, in IEEE/OES Autonomous Underwater Vehicles Symposium (AUV), 2020.
  
  \item Jun-Sik Kim, \underline{\textbf{Myung-Hwan Jeon}}, and Jung-Min Park, “Multi-Hand Direct Manipulation of Complex Constrained Virtual Objects”, in IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2019.
  
  \item \underline{\textbf{Myung-Hwan Jeon}}, Yeongjun Lee, Young-Sik Shin, Hyesu Jang, and Ayoung Kim, “Underwater Object Detection and Pose Estimation using Deep Learning”, in 12th IFAC Conference on Control Applications in Marine Systems, Robotics, and Vehicles (CAMS), 2019.

\end{pubSubsection}

\begin{pubSubsection}{Domestic Journal}

  \item Jaeho Shin, \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “Infrared Visual Inertial Odometry via Gaussian Mixture Model Approximation of Thermal Image”, in Journal of Korea Robotics Society (KROS), To be appeared.
  
  \item Wooseong Yang, \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “Noise Removal of FMCW Scanning Radar for Single Sensor Performance Improvement in Autonomous Driving”, in Journal of Korea Robotics Society (KROS), To be appeared.

  \item Jeongyun Kim,\underline{\textbf{Myung-Hwan Jeon}}, and Ayoung Kim, “Enhancing Single Thermal Image Depth Estimation via Multi-Channel Remapping for Thermal Images”, in Journal of Korea Robotics Society (KROS), 2022.
  
  \item\underline{\textbf{Myung-Hwan Jeon}}, Yeongjun Lee, Young-Sik Shin, Hyesu Jang, Taekyeong Yeu, and Ayoung Kim, “Synthesizing Image and Automated Annotation Tool for CNN based Under Water Object Detection”, in Journal of Korea Robotics Society (KROS), 2019.
  
\end{pubSubsection}

\begin{pubSubsection}{Dissertations}
  \item \underline{\textbf{Myung-Hwan Jeon}}, Ambiguity-Aware Multi-Object Pose Optimization toward Visually-Assisted Robot Manipulation. PhD thesis, \acf{KAIST}, 2022.
  
  \item \underline{\textbf{Myung-Hwan Jeon}}, Learning-Based Object Detection and 6D Pose Estimation toward Vision-Based Underwater Robotic Grasping. Master's thesis thesis, \acf{KAIST}, 2020.
  
\end{pubSubsection}

\begin{pubSubsection}{Other Publications}

  \item Jaeho Shin, \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “Infrared Visual-Inertial Odometry via Gaussian Mixture Model Approximation of Thermal Image Histogram ”, in Late-Breaking Results Poster on IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2023.  
  
  \item Wooseong Yang, \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “Azimuth-aware Noise Removal of FMCW Scanning Radar”, in Late-Breaking Results Poster on IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2023.  

  \item \underline{\textbf{Myung-Hwan Jeon}} and Ayoung Kim, “Measuring Prediction Reliability on 6D Object Pose Estimation”, in Late-Breaking Results Poster on IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2022.  

  \item \underline{\textbf{Myung-Hwan Jeon}}, Yeongjun Lee, Young-Sik Shin, Hyesu Jang, and Ayoung Kim, “Deep Learning Based Underwater Object Detection and Pose Estimation”, in Workshop on IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2018.

\end{pubSubsection} 



% \begin{pubSubsection}{Domestic Conference}
% \end{pubSubsection}


\end{rSection}

